\textsf{Are large language models superhuman chemists?}

### 2024-03-25 src/tex/ms.tex
for example -> e.g.

\section{Discussion and Conclusions}
Our findings show why \glspl{llm} are catching the interest of scientists across domains, but also the attention of the general public.
As observed, leading models outperform domain experts in chemistry questions on a majority of topics.
Unsurprinsigly, there are still striking limitations. 
First, it is important to note that the models are not able to estimate their own limitations.
Moreover, on very relevant topics (such as GHS classification) the answers provided by the models are mostly inaccurate.
Looking in more detail at the relationship between the model performance and the question type/source revealed that the studied models perform well on textbook questions, while underperforming on questions that require more reasoning (for example questions that require calculations).

>>>>

\section{Discussion and Conclusions}
Our findings show why \glspl{llm} are catching the interest of scientists across domains, but also the attention of the general public.
As observed, leading models outperform domain experts in chemistry questions on a majority of topics.
Unsurprinsigly, there are still striking limitations. 
First, it is important to note that the models are not able to estimate their own limitations.
Moreover, on very relevant topics (such as GHS classification) the answers provided by the models are mostly inaccurate.
Looking in more detail at the relationship between the model performance and the question type/source revealed that the studied models perform well on textbook questions, while underperforming on questions that require more reasoning (e.g. questions that require calculations).
